---
title: "Project report - Statistical Inference"
author: "Kirty Vedula"
date: "04/24/2015"
output: pdf_document
---
## Libraries
``` {r libraries}
library(datasets)
library(ggplot2)
library(knitr)
library(markdown)
```

## Simulating exponential distribution with rexp commmand
```{r setting_up}
set.seed(3)
lambda <- 0.2
num_sim <- 1000
sample_size <- 40
sim <- matrix(rexp(num_sim*sample_size, rate=lambda), num_sim, sample_size)
row_means <- rowMeans(sim)
```

## ------------------------------------------------------------------------
## Plot the histogram of averages
###Density of the averages of samples
###Theoretical center of distribution
``` {r histogram_averages}
hist(row_means, breaks=50, prob=TRUE,
     main="Distribution of averages of samples,
     drawn from exponential distribution with lambda=0.2",
     xlab="")
lines(density(row_means))
abline(v=1/lambda, col="red")
xfit <- seq(min(row_means), max(row_means), length=100)
yfit <- dnorm(xfit, mean=1/lambda, sd=(1/lambda/sqrt(sample_size)))
lines(xfit, yfit, pch=22, col="red", lty=2)
legend('topright', c("simulation", "theoretical"), lty=c(1,2), col=c("black", "red"))
```

## ------------------------------------------------------------------------
## Quantile plot for the row means calculated
``` {r quantile_mean}
qqnorm(row_means)
qqline(row_means)
```

## ------------------------------------------------------------------------
```{r simulated_mean}
lambda_vals <- seq(4, 6, by=0.01)
coverage <- sapply(lambda_vals, function(lamb) {
    mu_hats <- rowMeans(matrix(rexp(sample_size*num_sim, rate=0.2),
                               num_sim, sample_size))
    ll <- mu_hats - qnorm(0.975) * sqrt(1/lambda**2/sample_size)
    ul <- mu_hats + qnorm(0.975) * sqrt(1/lambda**2/sample_size)
    mean(ll < lamb & ul > lamb)
})
```

``` {r qplot}
qplot(lambda_vals, coverage) + geom_hline(yintercept=0.95)
```
## ------------------------------------------------------------------------
## Part 2

This part performs an exploratory data analysis of at least a single plot or table highlighting basic features of the data.
```{r plotting}
ggplot(data=ToothGrowth, aes(x=as.factor(dose), y=len, fill=supp)) +
  geom_bar(stat="identity",) +
  facet_grid(. ~ supp) +
  xlab("Dose in miligrams") +
  ylab("Tooth length") +
  guides(fill=guide_legend(title="Supplement type"))
```

## Fitting a model using dose and supplements as features
```{r fit_model}
fit <- lm(len ~ dose + supp, data=ToothGrowth)
summary(fit)
```

## ------------------------------------------------------------------------
## Confidence interval for the fit
```{r conf_int}
confint(fit)
```
